Literature review of Formal Methods applied to Blockchain technology

### 2022-01-13 article/article.tex
faulty states section

On a consensus rule, fault tolerances requirements are of utmost importance, including the collusion of nodes to alter a ledger.
In~\cite{Kawahara2020}, the author discusses a way to describe these tolerances with a scalable verification.

>>>>

On a consensus rule, fault tolerances requirements are of utmost importance, including the collusion of nodes to alter a ledger.
In~\cite{Kawahara2020}, the author discusses a way to formally describe these tolerances with a scalable verification.

Endorsement policies, the rule that define the criteria of agreement os transaction results between nodes, can be described
as a threshold function as follows:

\begin{displaymath}
  T(m,\textrm{node}_1,... ,\textrm{node}_n), m \in \mathbb{N}
\end{displaymath}
\linebreak[1]

Where $T(2,\textrm{node}_1,\textrm{node}_2,\textrm{node}_3)$ would be an endorsement policy
that means "among the three nodes in the argument, at least two nodes must return the same execution result".
With this, we can mathematically model faulty state verification.

\subsection{Faulty states}
Let $\mathbb{B}$ and $\mathbb{N}$ be sets of Boolean and natural numbers, respectively. The state of the \textit{i}-th node can be defined as:
$s_i = (s_i.e,s_i.v)$, where for each transaction execution, $s_i.e \in \mathbb{B}$ is the  existence of the result,
and $s_i.v \in \mathbb{B}$ is the value of the result (correct or wrong).

Using the threshold function previously shown, $T(m,s_1,... ,s_n) = (T.e,T.v)$. With this, let

\begin{displaymath}
  H_ = \left(\sum_{i}^{n} I(s_i.e \wedge (s_i.v = b)) \geq m \right)
\end{displaymath}

\begin{enumerate}
  \item[$\blacksquare$] \textit{m} is a treshold
  \item[$\blacksquare$] $b \in \mathbb{B}$
  \item[$\blacksquare$] $I : \mathbb{B} \mapsto \{0,1\}$  is the indicator function
\end{enumerate}
\  \\ %fake break line

With the expression above, the author of~\cite{Kawahara2020} infers:

\begin{displaymath}
  T.e = H_{true} \vee H_{false},  T.v = \neg{H_{false}}
\end{displaymath}

The  endorsement policy $EP = (EP.e,EP.v)$ can be formed with \textit{T}. When $EP.e = \textrm{true}$, the policy
is considered accordingly followed and the involved ledger is updated with the value of $EP.v$.
